Likelihood free inference of the halo model parameters with group and clustering statistics of the simulations of galaxy mock catalogs

### 2016-01-05 halo/text/abc.tex
more stuff in the text

Inference of the cosmological parameters and understanding the formation of galaxies whitihn the context of large scale 
structure, requires understanding of the Galaxy-Halo connection. Halos are biased tracers of the large scale structure 
and galaxies reside dark matter Halos. Halo occupation distribution---HOD---is a probabilistic framework that describes how 
galaxies populate dark matter halos. The central tenet of HOD modeling is that the probability of $N$ galaxies residing a 
dark matter halo is determined by the mass of the host halo. This statistical prescription for connection of galaxies and halos 
has been successful in reproducing the galaxy two-point clustring as well as the galaxy-matter cross correlation---galaxy-galaxy 
lensing---within the context of the halo model, and has been used in understanding teh co-evolution of galaxies and halos and putting 
constraints on th relation between the stellar mass and halo mass of galaxies.

>>>>

Inference of the cosmological parameters and understanding the formation of galaxies within the context of large scale 
structure, requires understanding of the Galaxy-Halo connection. Halos are biased tracers of the large scale structure 
and galaxies reside dark matter Halos. Halo occupation distribution---HOD---is a probabilistic framework that describes how 
galaxies populate dark matter halos. The central tenet of HOD modeling is that the probability of $N$ galaxies residing a 
dark matter halo is determined by the mass of the host halo. This statistical prescription for connection of galaxies and halos 
has been successful in reproducing the galaxy two-point clustring as well as the galaxy-matter cross correlation---galaxy-galaxy 
lensing---within the context of the halo model, and has been used in understanding teh co-evolution of galaxies and halos and putting 
constraints on th relation between the stellar mass and halo mass of galaxies.

In the context of large scale clustering of galaxies, inference of the cosmological and halo model parameters are performed assuming 
an analytical model for the two-point correlation function of the galaxies, and a gaussian likehood. This Gaussian likelihood approximates 
the probability of observing the data---observed positions of the galaxies in the configuration space---given the halo model by computing 
the squared difference of the two-point correlation function measured from the observations and the analytical model for the galaxy 
clustering, weighted by a covariance matrix. The weighted difference of the number density of the observed galaxies and the analytical 
number density is often added to this.

Hogg writes why we do not want to do this .....

Approximate bayesian computation (ABC) provides a framework that alleviates the issues arising from approximating the likelihood of 
observing the large scale population of galaxies given the cosmological and halo model parameters. ABC approximates the posterior 
probability distribution function over the model parameters given the data---the angular positions of the galaxies on the sky and 
their redshifts---by drawing proposals from the prior over the model parameters, simulating the data with the proposals, and rejecting 
the proposals for which the distance between the data and the simulation (measured by a metric) is less than a certain threshold. The 
procedure described here is rejected sampling. In practice rejected sampling is expensive and instead, investigators change start 
by sampling from the prior with a large ..........
